|

### 2021-10-16 article/article.Rmd
edit citation article

Our findings have implications that extend well beyond Brazil. As several countries have local city councils and multiparty systems, the dynamics we expose here may explain how fragmented legislatives are not synonymous with policy paralysis. This runs in contrast with well-established theories that point out that multipartism may be a peril to democratic regimes \citep{mainwaring1993presidentialism, stepan1993constitutional}. Additionally, our findings may help us understand why other countries in Latin America and Asia can generate effective governance despite having strong executives and large coalitions \citet{pereira2012surprising}.

>>>>

Our findings have implications that extend well beyond Brazil. As several countries have local city councils and multiparty systems, the dynamics we expose here may explain how fragmented legislatives are not synonymous with policy paralysis. This runs in contrast with well-established theories that point out that multipartism may be a peril to democratic regimes \citep{mainwaring1993presidentialism, stepan1993constitutional}. Additionally, our findings may help us understand why other countries in Latin America and Asia can generate effective governance despite having strong executives and large coalitions \citep{pereira2012surprising}.
